Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-18 paper-2023-acsos-pulverization.tex
pass on IVA complete

The configuration produced by the \ac{dsl} needs a platform that instructs the system on the way actual communication needs to be performed.
%
In our current implementation,
we provide out of the box a JVM platform based on the MQTT protocol
and supporting both intra- and inter-device communication.
%
For the large scale experiment,
we implemented a second platform,
this time to comply with the requirements of the simulation engine we used.
%
The implementation required little effort,
and it has been made available as part of the evaluation repositories.

@@

The system is composed of two kinds of device: \emph{wearable} and \emph{alert}.
%
Wearables consist of the following pulverised components:
sensors ($\sigma^w$), perceiving other devices by their signal strength;
behaviour ($\beta^w$), converting raw data from the sensor into messages for the alert system; and
communication ($\chi^w$) sending data to the alert system.
%
They do not need state nor actuators.
%
The alert consists of the following pulverized components:
$\beta^a$, computing the mean distance among devices;
$\kappa^a$, storing the distances measured by the device;
%\meta{
%    NICOLAS what does this do? write within this meta block.
%    %
%    Hold in memory the updated distances between the devices.
%};
$\chi^a$, responsible for receiving the data from the wearable devices;
$\alpha^a$, enacting the alarm by showing a color on the screen.
%
It needs no sensors.

We use the following hosts in the scenario:
\begin{itemize}
    \item multiple \emph{Smartphones} used by the people to detect the distance from the others;
    \item a \emph{Monitor} used to show the alarm in the laboratory;
    \item a \emph{Server} used run the crowd algorithm and the wearable logic.
\end{itemize}

Initially, $\beta^{w}$ is allocated to the \emph{Server} while
$\sigma^{w}$ and $\chi^{w}$ are executed on the \emph{Smartphones},
and all the \emph{alert} components are executed in the \emph{Monitor}.
%
In the experiment,
we define a rule by which,
if the \emph{Server} is overloaded,
$\beta^{w}$ is moved to the \emph{Smartphones}
(with each smartphone running the $\beta^{w}$ corresponding to its $\sigma^{w}$).
%
During the experiment,
we launch several heavy-duty processes on the \emph{Server},
and we observe how the system reacts to the overload.

Given the infrastracture defined above, we simulate also a condition where the \emph{Server} is overloaded and, via pulverization,
we want to lighteninig the load of the \emph{Server} by moving the $\beta_{werable}$ in the \emph{Smartphones}.
%
Formally, we can write the reconfiguration event as follow: $\beta^{werable}_{server} \xrightarrow{\mathcal{E}} \beta^{werable}_{smartphone}$
where $\mathcal{E}$ represents the reconfiguration event due to the high load in the \emph{Server}.

At the start of the system, each \emph{Wearable} device, with the $\sigma$ component,
start to perceive the other devices in the laboratory using the RSSI signal from the Bluetooth.
%
The $\beta$ component, initially executed in the \emph{Server}, starts to compute the distances from the other devices
based on the received RSSI signal from the $\sigma$ component.
%
Once the distances are computed, the $\chi$ component sends the data to the
\emph{Laboratory} containing the distances perceived by the device.
%

Similarity, the \emph{Laboratory} device has all the components executed in the \emph{Local PC},
where the $\chi$ component receives the data from the \emph{Wearable},
the $\beta$ component computes the mean distance between the devices.
%
The $\kappa$ component persist in memory the updated devices graph based on the distances retrieved by the $\chi$ component.
and the $\alpha$ component show in the monitor the color based on the mean distance computed by the $\beta$ component.

As soon as the reconfiguration event is triggered, the $\beta$ component of the \emph{Wearable} is moved from the \emph{Server} to the \emph{Smartphone}
lightening the server and preserving from one side the functional semantic of the system and from the other side maintain the system operational.
%
The reconfiguration of the system in entirely managed by the framework, which handle all the machinery and communication to move the component from
one host to another.
%
With this simple example we show how the pulverization framework can be used in practice to manage a system with different devices and an heterogeneous
infrastructure.
%
Moreover, we show how the pulverization framework can be used adapt the system to changing requirement without loosing the functional semantic of the system
by describing the system in a declarative way.

>>>>

The configuration produced by the \ac{dsl} needs a platform that instructs the system on the way actual communication needs to be performed.
%
In our current implementation,
we provide out of the box a JVM platform based on the MQTT protocol
supporting both intra- and inter-device communication.
%
The platform also feature an optimization for pulverized components of the same logical device ending up running on the same host:
as it would be expected,
they would communicate directly by sharing memory,
without the need to go through (de)serialisation processes and networking.
\meta{NICOLAS please check if the last sentence is true, if so remove this comment}
%
For the large scale experiment,
we implemented a second platform,
this time to comply with the requirements of the simulation engine we used.
%
The implementation required little effort,
and it has been made available as part of the evaluation repositories.

@@

The system is composed of two kinds of device: \emph{wearable} and \emph{alert}.
%
Wearables consist of the following pulverised components:
sensors ($\sigma^w$), perceiving other devices by their signal strength;
behaviour ($\beta^w$), converting raw data from the sensor into messages for the alert system; and
communication ($\chi^w$) sending data to the alert system.
%
They do not need state nor actuators.
%
The alert consists of the following pulverized components:
$\beta^a$, computing the mean distance among devices;
$\kappa^a$, storing the distances measured by the device for comparison with the recent past;
%\meta{
%    NICOLAS what does this do? write within this meta block.
%    %
%    Hold in memory the updated distances between the devices.
%};
$\chi^a$, responsible for receiving the data from the wearable devices;
$\alpha^a$, enacting the alarm by showing a color on the screen.
%
It needs no sensors.

We use the following hosts in the scenario:
\begin{itemize}
    \item multiple \emph{Smartphones}, one per user, emulating wearables and used as distance sensors;
    \item a \emph{Monitor} used to show the alarm;
    \item a \emph{Server} used run crowd estimation and wearable logic.
\end{itemize}

Initially, $\beta^{w}$ is allocated to the \emph{Server} while
$\sigma^{w}$ and $\chi^{w}$ are executed on the \emph{Smartphones},
and all the \emph{alert} components are executed in the \emph{Monitor}.
%
In the experiment,
we define a rule by which,
if the \emph{Server} is overloaded,
$\beta^{w}$ is moved to the \emph{Smartphones}
(with each smartphone running the $\beta^{w}$ corresponding to its $\sigma^{w}$).
%
During the experiment,
we launch several heavy-duty processes on the \emph{Server},
and we observe how the system reacts to the overload.
%
We rely on the MQTT platform module for all the communication,
meaning that both intra- and inter-device communication is handled by the same protocol and broker.

As soon as the reconfiguration event is triggered,
the $\beta$ component of the \emph{Wearable} is moved from the \emph{Server} to the \emph{Smartphone} $s$ hosting $\sigma^{w}_{s}$,
relieving the server and preserving while retaining the system in nominal conditions.
%
The reconfiguration of the system in entirely managed by the framework,
which handles all the machinery and communication to move the component from
one host to another.

This example has been used as a real-world testbed driving our experimental implementation.
%
For the sake of brevity,
we do not report the entire configuration in this manuscript, but it is available in the companion artifact~\cite{TBD}
\meta{
    NICOLAS please replace TBD with the artifact citation from zenodo. Use doi2bib to get the bibtex entry.
}
for those willing to exercise the whole system.
%
To simplify testing we also provide,
in the same artifact,
a simulation of the system where every device is containerized.
